Transparent Changes

### 2022-05-02 scripts/comparison.Rmd
Update comparison script

# Functions to calculate VO2max using different strategies

@@

# Binned time average
max_time_binned <- function(data, parameter) {
  nbin <- ceiling(nrow(data) / parameter)
  ibins <- seq(from = 1, by = parameter, length.out = nbin)
  binmean <- function(i, length, data) {
    values <- data$VO2_rel[i:(i + length - 1)]
    values[is.na(values)] <- 0
    mean(values)
  }
  binmeans <- purrr::map_dbl(.x = ibins, .f = binmean, length = parameter, data = data)
  max(binmeans)
}

@@

@@

## Plot data

```{r}
quant <- function(data, lower, upper) {
  qs <- quantile(data, probs = c(lower, upper), names = FALSE)
  data.frame(
    ymin = qs[[1]],
    ymax = qs[[2]]
  )
}

@@

## Respiratory Rate over time

```{r}
read_rr <- function(file) {
  dat <- spiro(file)
  # Zero-lag Butterworth filter
  rr <- spiro_smooth(dat, smooth = "fz", columns = "RR")[, 1]
  time <- attr(dat, "raw")$time
  load <- attr(dat, "raw")$load

  filename_split <- strsplit(file, "/")[[1]]
  id <- filename_split[length(filename_split)]

@@

>>>>

## Functions to calculate VO2max using different strategies

@@

# Binned time average
max_time_binned <- function(data, parameter, max = TRUE) {
  nbin <- ceiling(nrow(data) / parameter)
  ibins <- seq(from = 1, by = parameter, length.out = nbin)
  binmean <- function(i, length, data) {
    values <- data$VO2_rel[i:(i + length - 1)]
    values[is.na(values)] <- 0
    mean(values)
  }
  binmeans <- purrr::map_dbl(.x = ibins, .f = binmean, length = parameter, data = data)
  if (max) max(binmeans) else binmeans
}

@@

## Iterate over all exercise tests

@@

## Plot data: Comparison of processing strategies

```{r}
# Function for calculating quantils
quant <- function(data, lower, upper) {
  qs <- quantile(data, probs = c(lower, upper), names = FALSE)
  data.frame(
    ymin = qs[[1]],
    ymax = qs[[2]]
  )
}

@@

## Plot: Respiratory Rate over time

```{r}
read_rr <- function(file) {
  dat <- spiro(file)
  # Zero-lag Butterworth filter with default parameters
  rr <- spiro_smooth(dat, smooth = "fz", columns = "RR")[, 1]
  time <- attr(dat, "raw")$time
  load <- attr(dat, "raw")$load

  # file id
  filename_split <- strsplit(file, "/")[[1]]
  id <- filename_split[length(filename_split)]

@@

# Plot: Example of different strategies

```{r}
id <- 46
id_info <- read.csv("../data/participants.csv")
bodymass <- id_info$bodymass[id_info$p == id]

exm_data <- spiro(files[id])
raw_vo2 <- attr(exm_data, "raw")$VO2
raw_time <- attr(exm_data, "raw")$time
fz <- spiro_smooth(exm_data, "fz", "VO2")[,1]
mb <- spiro_smooth(exm_data, "30b", "VO2")[,1]
mt <- spiro_smooth(exm_data, 30, "VO2")[,1]
tb <- max_time_binned(exm_data, 30, max = FALSE) * attr(exm_data, "info")[["weight"]]
rb_time <- seq(from = 15, by = 30, length.out = length(tb))

exm_tidy <- data.frame(
  method = c(rep.int("raw", length(raw_vo2)), rep.int("fz", length(fz)), rep.int("mb", length(mb)), rep.int("mt", length(mt)), rep.int("tb", length(tb))),
  value = c(raw_vo2, fz, mb, mt, tb),
  time = c(rep.int(raw_time, 3), seq_along(mt), rb_time)
)

exm_tidy$method <- factor(
  exm_tidy$method, 
  levels = c("raw", "mb", "mt", "tb", "fz"), 
  labels = c("raw", "Moving Breath", "Moving Time", "Binned Time", "Digital Filter")
)
exm_tidy$value <- exm_tidy$value / bodymass

ggplot(exm_tidy, aes(x = time)) +
  geom_point(data = exm_tidy[exm_tidy$method == "raw", ], aes(y = value), alpha = 0.1) +
  geom_line(data = exm_tidy[exm_tidy$method %in% c("Moving Time", "Moving Breath", "Digital Filter"), ], aes(y = value, color = method), size = 0.7) +
  geom_point(data = exm_tidy[exm_tidy$method == "Binned Time", ], aes(y = value, fill = method), color = met.brewer("Java", 3)[3], size = 1.2) +
  scale_x_continuous(
    name = "Time (min)",
    limits = c(500,850),
    breaks = c(540, 630, 720),
    labels = c(8, 10, 12),
    expand = c(0,0)
  ) +
  scale_y_continuous(
    name = "VO2 (ml/min/kg)",
    limits = c(55,75)
  ) +
  scale_color_manual(
    name = "",
    values = c(met.brewer("Java", 3)[1:2], "blue")
  ) +
   scale_fill_manual(
    name = "",
    values = "white"
  ) +
  theme_classic() +
  theme(
    legend.position = c(0.9, 0.55),
  )

ggsave(filename = "../plots/example.png", width = 6, height = 4, dpi = 1200, bg = "white")
```
